Simultaneous Elicitation of Scoring Rule and Agent Preferences for Robust Winner Determination

### 2021-01-12 minimax.tex
ID

\author{
	Beatrice Napolitano$^1$\footnote{Contact Author}\and
	Olivier Cailloux$^1$\and
	Paolo Viappiani$^2$\\
	\affiliations
	$^1$Université Paris-Dauphine, Université PSL, CNRS, LAMSADE\\
	$^2$LIP6, UMR 7606, CNRS and Sorbonne Universit\'e\\
	\emails
	\{beatrice.napolitano, olivier.cailloux\}@dauphine.fr,
	paolo.viappiani@lip6.fr
}

>>>>

\author{ID: 3177}

%\author{
%	Beatrice Napolitano$^1$\footnote{Contact Author}\and
%	Olivier Cailloux$^1$\and
%	Paolo Viappiani$^2$\\
%	\affiliations
%	$^1$Université Paris-Dauphine, Université PSL, CNRS, LAMSADE\\
%	$^2$LIP6, UMR 7606, CNRS and Sorbonne Universit\'e\\
%	\emails
%	\{beatrice.napolitano, olivier.cailloux\}@dauphine.fr,
%	paolo.viappiani@lip6.fr
%}
